Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
changes to extensional

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state, the extensional background
flow is started.  We use this example to characterize the required
extensional rate to overcome the adhesive forces at for vesicles with
different reduced areas.  For all the simulations, the length of the
vesicles are fixed, while the area is changed to achieve the desired
reduced area.

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.03$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.1$.  After time $t=400$, the
  vesicles extensional rate has overcome the adhesive force, and the
  vesicles continue to separate.}
\end{figure}

>>>>

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state doublet, the extensional
background flow is started.  We use this example to characterize the
required extensional rate to overcome the adhesive forces of the
doublet.  In particular, we investigate the effect of the reduced area.
For all the simulations, the length of the vesicles are fixed, while the
area is changed to achieve the desired reduced area.

We observe three different vesicle configurations that depend on the
reduced area and extensional rate.  First, the doublet is not broken and
the individual vesicles long axis is parallel to the contracting
direction (Figure~\ref{fig:extensional1}).  Second, the doublet is not
broken, but it tilts to some inclination angle that is not parallel to
either of the contracting or separation directions
(Figure~\ref{fig:extensional3}).  Finally, if the extensional rate is
sufficiently large, the doublet is broken and the vesicles tend to
$(0,\pm \infty)$.

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.03$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.
  After time $t=400$, the vesicles extensional rate has overcome the
  adhesive force, and the vesicles continue to separate.}
\end{figure}
